---
title: "Covid in Georgia"
author: "Josephine Walker"
date: "31/07/2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Intro

Georgia reported their first confirmed case of Covid-19 on 26 February 2020. As of 2 July 2020, only 939 confirmed cases and 15 deaths have been reported. The success of Georgia's limitation of spread of Covid-19 can be attributed to early non-pharmaceutical interventions including closing schools (early March), closing borders and mandatory quarantining of international arrivals, lockdown of individual affected areas (late March) and full lockdown throughout the country (30 March). Alongside this, they have implemented extensive contact tracing and testing, and all confirmed cases are treated in hospital. There is regular screening of key workers. As of 2 July 2020, 117,701 PCR tests for Covid-19 have been conducted, a rate of more than 30,000 tests per million population. 

Here we use test data and contact tracing data collected by the National Center for Disease Control (NCDC) in Georgia to characterize the epidemic in Georgia. This includes demographics of those infected compared to the general population, symptom and death rates by age, and rates of transmission to different types of contacts. We also calculate the secondary attack rate for different types of contacts and overall number of secondary cases per primary case (observed reproductive number).

##  Methods

### Data collection

- Types of test used, criteria for testing (case identification).
  - A variety of test types were used, here we present the results from antigen tests confirming current infection, primarily real time PCR tests. [In the database as confirmation test result]
  - Data exported on 24 June 2020 [match numbers in intro to data we have]
- More detail on policies - maybe in a figure
- Ethics waiver from NCDC and registered in Bristol

### Analysis

- De-identified personal IDs used to link contact tracing database to confirmed cases
- Data cut off date 24 June 2020
- Analysis conducted in R
- Can we compare demographics of infection to national demographics? geostat or other source?


## Results



```{r readdat,warning=FALSE}
setwd("~/git/covid-georgia/")

library(readxl)
library(lubridate)
library(dplyr)

tcols <- c("skip","skip","skip","text","logical","date",rep("text",7),"date","text","text","date",rep("text",8),"date","text","text")
testing <- read_xlsx("./data/testing2020-06-24.xlsx",col_types=tcols)


hcols <- c("skip","text","text","numeric","numeric","numeric","text","numeric",rep("text",6),"date","date","skip","text","text","text","date",rep("text",13),"skip","text","skip","text","text","text","skip","text","text",rep("text",36))
hospital <- read_xlsx("./data/COVID19treated.xlsx",col_types=hcols)

ccols <- c("")
contacts <- read_xlsx("./data/contacts30June_updated.xlsx",skip=1)
```


```{r cleandat} 




```


### Table of demographics of those infected (treated database)
Hospitalization data and comorbidities were available for `r nrow(hospital)` diagnosed patients with hospitalization dates ranging from `r min(hospital$hospdate,na.rm=T)` to `r max(hospital$hospdate,na.rm=T)`. Could add more detail here on particular symptoms if of interest.

```{r treated}
# hospital$`Hospitalization date (day / month / year)`
hospital$length <- hospital$`discharge date (day / month / year)` - hospital$`Hospitalization date (day / month / year)`
hospital$diagnosisdate <- as.Date(hospital$`Date of diagnosis`,format = "%d.%m.%Y") 
hospital$hospdate <- as.Date(hospital$`Hospitalization date (day / month / year)`) 
hospital$hosplag <- hospital$hospdate - hospital$diagnosisdate
hospital$outcome <- as.factor(hospital$`The result of hospitalization`)



library(data.table)
library(arsenal)

# Customizing the table
my_controls <- tableby.control(
  test = T,
  total = T,
  numeric.test = "kwt", cat.test = "chisq",
  numeric.stats = c("meansd", "medianq1q3", "range", "Nmiss2"),
  date.test = "kwt",
  date.stats=c("Nmiss","median","range"),
  cat.stats = c("countpct", "Nmiss2"),
  stats.labels = list(
    meansd = "Mean (SD)",
    medianq1q3 = "Median (Q1, Q3)",
    range = "Min - Max",
    Nmiss2 = "Missing"
  )
)

my_labelsH <- list(
  Age = "Age (years)",
  `Age group` = "Age group",
  Gender = "Gender",
  length = "Length of hospital stay",
  hosplag = "Time from diagnosis to hospitalization",
  `reffered to intensive care` = "Intensive care",
  `Severity of the disease` = "Disease severity",
  diagnosisdate = "Diagnosis date",
  `Hospitalization date (day / month / year)` = "Hospitalization date",
  `Place of exposure - country` = "Place of exposure", # also have region of Georgia
  `Medical staff` = "Medical staff",
  `Asymptomatic` = "Asymptomatic",
  outcome = "Outcome"
) # Lots more to add

tableH <- tableby(Gender ~ .,
  data = hospital[,c("Age","Age group","reffered to intensive care","Severity of the disease","Gender","length","outcome","diagnosisdate", "Place of exposure - country","Asymptomatic")], #"Hospitalization date (day / month / year)","hosplag",
  control = my_controls
)
 
knitr::kable(summary(tableH,
  labelTranslations = my_labelsH,
  title = "Characteristics of COVID-19 patients"
))



```

###Table of demographics of those tested (tested database)

A total of `r dim(testing[!is.na(testing$"Confirmation Test Result"),])[1]` antigen (PCR) test results were available, with `r  length(unique(testing$PersonalID[!is.na(testing$"Confirmation Test Result")]))` unique individual patient IDs recorded. 


```{r tested}
testing$BirthDate2 <- as.Date(testing$BirthDate)
max(testing$BirthDate2,na.rm=T)
min(testing$BirthDate2,na.rm=T)
testing$BirthDate2[testing$BirthDate2 >= as.Date("2020-07-01")] <- NA
testing$BirthDate2[testing$BirthDate2 <= as.Date("1915-07-01")] <- NA
# sum(is.na(testing$BirthDate))
# sum(is.na(testing$BirthDate2)) # 42 different
testing$Age <- as.numeric(floor((as.Date("2020-07-01")-testing$BirthDate2)/365))

## not sure about this
# testing$Testname2 <- as.factor(testing$`Test Name`)
# levels(testing$Testname2)
# testing$rtPCR <- ifelse(as.numeric(testing$Testname2) %in% c(1,3,4,7),TRUE,FALSE)

testingF <- testing %>% filter(!is.na(`Confirmation Test Result`))

TU <- unique(testingF$PersonalID)
testingU <- testingF %>% arrange(PersonalID,`Test Date`) %>% group_by(PersonalID) %>% summarise(IsForeigner=first(IsForeigner),Age=first(Age),Gender=first(Gender),Fever=first(Fever),Cough=first(Cough),`Risk Group`=first(`Risk Group`),`Confirmation Test Result` = first(`Confirmation Test Result`))

my_labelsT <- list(
  Foreigner = "IsForeigner",
  Age = "Age",
  Gender = "Gender",
  Fever = "Fever",
  Cough = "Cough",
  `Risk group` = "Risk Group",
  `Test result` = "Confirmation Test Result"#,
  # Country = "Country"
  ) 

tableT <- tableby(`Confirmation Test Result` ~ .,
  data = testingF[,c("Age","Gender","Fever","Cough","Risk Group","Confirmation Test Result","IsForeigner")], 
  control = my_controls
)
 
knitr::kable(summary(tableT,
  labelTranslations = my_labelsT,
  title = "Characteristics of COVID-19 tests"
))


tableTU <- tableby(`Confirmation Test Result` ~ .,
  data = testingU[,c("Age","Gender","Fever","Cough","Risk Group","Confirmation Test Result","IsForeigner")], 
  control = my_controls
)
 
knitr::kable(summary(tableTU,
  labelTranslations = my_labelsT,
  title = "Characteristics of COVID-19 testing - unique patient IDs"
))


```

## Contact networks

Index cases summary

```{r contacts,echo=TRUE}
contacts$missingPatID <- is.na(contacts$`Patient unique ID`)
contacts$missingPatID[contacts$missingPatID] <- 1:sum(contacts$missingPatID)
contacts$newPatID <- ifelse(is.na(contacts$`Patient unique ID`),paste("missingP",contacts$missingPatID,sep=""),contacts$`Patient unique ID`)

contacts$missingCID <- is.na(contacts$`Contact ID`)
contacts$missingCID[contacts$missingCID] <- 1:sum(contacts$missingCID)
contacts$newCID <- ifelse(is.na(contacts$`Contact ID`),paste("missingC",contacts$missingCID,sep=""),contacts$`Contact ID`)

contacts$case <- as.factor(contacts$`Confirmed Case`)
levels(contacts$case) <- c(FALSE,NA,TRUE)

contacts$Age[contacts$Age=="*"] <- NA
contacts$Age <- as.numeric(contacts$Age)
contacts$Gender[contacts$Gender=="male"] <- "Male"
# rate of transmission by type of contact

contactsType <- contacts %>% filter(`Contact type`!="unknown")
contactsType$Coworker <- contactsType$`Contact type`=="Co-worker"
contactsType$Family <- contactsType$`Contact type`=="Family member"
contactsType$Friend <- contactsType$`Contact type`=="Friend"
contactsType$Medical <- contactsType$`Contact type`=="Medical Personnel"
contactsType$Neighbour <- contactsType$`Contact type`=="Neighbour"

mType <- glm(data=contactsType,case ~ `Contact type`,family=binomial)
summary(mType)

mType2 <- glm(data=contactsType,case ~ Family,family=binomial)
summary(mType2)

mType3 <- glm(data=contactsType,case ~ Coworker,family=binomial)
summary(mType3)

mType4 <- glm(data=contactsType,case ~ Friend,family=binomial)
summary(mType4)

mType5 <- glm(data=contactsType,case ~ Medical,family=binomial)
summary(mType5)

mType6 <- glm(data=contactsType,case ~ Neighbour,family=binomial)
summary(mType6)

####
# age and gender of index case
mAS <- glm(data=contacts,case ~ Age + Gender, family=binomial)
summary(mAS)
mA <- glm(data=contacts,case ~ Age , family=binomial)
summary(mA)
mS <- glm(data=contacts,case ~ Gender, family=binomial)
summary(mS)


### merge contacts with screening data
testsub <- testingU %>% filter(!is.na(PersonalID)) %>% select(PersonalID,Gender,Age)

contact.merge <- left_join(contacts,testsub,by=c("Contact ID"="PersonalID"))
contactsType.m <- contact.merge %>% filter(`Contact type`!="unknown")
contactsType.m$Coworker <- contactsType.m$`Contact type`=="Co-worker"
contactsType.m$Family <- contactsType.m$`Contact type`=="Family member"
contactsType.m$Friend <- contactsType.m$`Contact type`=="Friend"
contactsType.m$Medical <- contactsType.m$`Contact type`=="Medical Personnel"
contactsType.m$Neighbour <- contactsType.m$`Contact type`=="Neighbour"


m2 <- glm(data=contact.merge,case ~ Age.x + Age.y,family=binomial)
summary(m2)

m3 <- glm(data=contact.merge,case ~ Age.x + Age.y + Gender.x + Gender.y + `Contact type`,family=binomial)
summary(m3)

m4 <- glm(data=contactsType.m,case ~ Age.x + Age.y + Gender.x + Gender.y + Coworker + Family + Friend + Medical + Neighbour,family=binomial)
summary(m4)

m5 <- glm(data=contactsType.m,case ~  Age.y + Coworker + Family + Friend + Medical,family=binomial)
summary(m5)


```

Rates of transmission by type of contact, gender and age of index case - table as in Bi

Contact by age groups and type of contact

```{r agegroups}
contact.merge$AgeGroup.X <- with(contact.merge,ifelse(Age.x < 10, "0-9",ifelse(Age.x < 20, "10-19",ifelse(Age.x < 30, "20-29",ifelse(Age.x < 40, "30-39",ifelse(Age.x < 50, "40-49",ifelse(Age.x < 60, "50-59",ifelse(Age.x < 70, "60-69","70+"))))))))

contact.merge$AgeGroup.Y <- with(contact.merge,ifelse(Age.y < 10, "0-9",ifelse(Age.y < 20, "10-19",ifelse(Age.y < 30, "20-29",ifelse(Age.y < 40, "30-39",ifelse(Age.y < 50, "40-49",ifelse(Age.y < 60, "50-59",ifelse(Age.y < 70, "60-69","70+"))))))))

d <- table(contact.merge$AgeGroup.X, contact.merge$AgeGroup.Y)
n <- table(contact.merge$AgeGroup.X, contact.merge$AgeGroup.Y,contact.merge$case)
n1 <- table(contact.merge$AgeGroup.X[contact.merge$case==TRUE], contact.merge$AgeGroup.Y[contact.merge$case==TRUE])
n2 <- table(contact.merge$AgeGroup.X[contact.merge$case==FALSE], contact.merge$AgeGroup.Y[contact.merge$case==FALSE])

n1/d
n2/d
```

Transmission by age groups and type of contact

Total number of secondary cases per primary case

```{r overall}
table(contacts$case)


```

Plot of contact network

```{r network}
library(igraph)




colors <- as.factor(contacts$`Confirmed Case`)
levels(colors) <-c( "blue","gray50","yellow")


edges <- as.matrix(contacts[,c("newPatID","newCID")])
g1 <- graph_from_edgelist(edges)

edge_attr(g1,"type") <- contacts$`Contact type`
edge_attr(g1,"transmission") <- colors

plot.igraph(g1,vertex.label=NA,edge.color=edge_attr(g1)$transmission,vertex.size=igraph::degree(g1)-1)



table(table(contacts$newPatID)) # 607 only have one contact (one row for that PID)
table(table(contacts$`Patient unique ID`,useNA = "ifany")) #357 have one contact so the NA are all added here of course.

g2 <- graph_from_edgelist(edges[!is.na(contacts$`Patient unique ID`),]) #2632 contacts 

g3 <- graph_from_edgelist(edges[!is.na(contacts$`Patient unique ID`) & !is.na(contacts$`Contact ID`),])

plot.igraph(g3,vertex.label=NA,vertex.size=3)


```




## Discussion

- main outcomes
- limitations of study
- comparison to other contact tracing studies (Bi, etc.)
- comparison to other countries in the region
- understanding how and why the response was able to be so strong (eg HCV testing and treatment infrastructure)